---
title: "170721_coursera_developing data product(week4)"
author: "Taesoon Kim"
date: "Jul-21-2017"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## Introduction and Assignment

  - This assignment is course project in Coursera lecture, Developing data product.
    + I will solve 2 questions
  - Question 1.
    + I have to use shiny() function, and share my server.R and ui.R
    + In my code, I receive various input values, and output is mpg text
  - Question 2.
    + I will make rmarkdown and use slidify() function
    + And share 5 page presentation in my github and Rpubs
  
## Slide with R Output

```{r load, echo=TRUE}
# Set the directory
setwd("D:/1-1. R studio/Lecture9. Developing data product/week4/170724_coursera_ddp")

# Load dataset
data(mtcars)

#check the "mtcars" data
str(mtcars)
```

```{r MPG,echo=TRUE}
# Focus on MPG and draw a histogram
summary(mtcars$mpg)  # mpg consists of numbers, I can check

# Draw a histogram with respect to MPG 

hist(mtcars$mpg,breaks=10,main="Freq. of Miles per Gallon",xlab="MPG")
```

The largest number of MPG data is located in the 14~16 range. And also I can check that manual transmission uses more gas than automatic transmission.

## Cross validation

```{r cross validataion,echo=TRUE}
# Separate the training data and testing data
set.seed(135)
library(ggplot2)
library(lattice)
library(caret)     # In order to use createDataPartition() function
inTrain<-createDataPartition(mtcars$mpg,p=0.6,list=FALSE)
training<-mtcars[inTrain,]
testing<-mtcars[-inTrain,]
dim(training)
dim(testing)
```

I use createDataPartition() function, and separate training data(60%) and testing data(40%). I am going to adjust various modeling methods using training data, since then check the results correct or not using testing data.


## Random forest

```{r random forest,echo=TRUE,include=TRUE}
# randomForest() function
library(randomForest)
rf_training<-randomForest(mpg~.,data=training,importance=TRUE)
rf_training

# draw a graph
varImpPlot(rf_training,main="varImpPlot of train data",cex=0.7)
```

Using random forest method, I will check which variable is the most effective in this data set. In this data set, disp is the most effective and wt, hp, cyl are also effective. 